Case Study: scRNA-seq (Mouse data, scDD method)

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Update headers, simplify p-val variable naming

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="meanExp", maxy=12,
           main = "MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="detection", maxy=12,
           main = "MAST, Covariate 2: Detection Rate") 
```

@@

### Covariate one: mean nonzero expression

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

>>>>

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="meanExp", maxy=16,
           main = "MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="detection", maxy=16,
           main = "MAST, Covariate 2: Detection Rate") 
```

@@

### Covariate one: Mean nonzero expression

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans = "log1p") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-scdd.Rmd
Update headers, simplify p-val variable naming

    res <- results(scDD(sce, 
             condition = "group",
             prior_param = list(alpha=0.01, mu0=0, s0=0.01, a0=0.01, b0=0.01), 
             testZeroes = TRUE,
             categorize = FALSE))
    rowData(dat)$scdd_p_nonzero <- res$nonzero.pvalue
    rowData(dat)$scdd_p_zero <- res$zero.pvalue
    rowData(dat)$scdd_p_combined <- res$combined.pvalue
  }else{
     message("scDD p-values already computed.")
  }
  return(dat)
}

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p_combined", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p_combined", covariate="meanExp", maxy=12,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p_combined", covariate="detection") + 
  ggtitle("scDD, Covariate 2: Detection Rate")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p_combined", covariate="detection", maxy=12,
           main = "scDD, Covariate 2: Detection Rate") 
```
## Multiple-Testing Correction

@@

### Covariate one: Mean expression

@@

if (!file.exists(res1)){
  sb1 <- bd %>% buildBench(data.frame(rowData(humandata)) %>% 
                                   na.omit() %>%
                                   mutate(pval=scdd_p_combined,
                                          ind_covariate=meanExp), 
                          ftCols = c("meanExp"),
                          parallel=TRUE)

@@

if (!file.exists(res2)){
  sb2 <- bd %>% buildBench(data.frame(rowData(humandata)) %>% 
                                   na.omit() %>%
                                   mutate(pval=scdd_p_combined,
                                          ind_covariate=detection), 
                          ftCols = c("detection"),
                          parallel=TRUE)

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

>>>>

    res <- results(scDD(sce, 
             condition = "group",
             prior_param = list(alpha=0.01, mu0=0, s0=0.01, a0=0.01, b0=0.01), 
             testZeroes = TRUE,
             categorize = FALSE))
    rowData(dat)$scdd_p <- res$combined.pvalue
  }else{
     message("scDD p-values already computed.")
  }
  return(dat)
}

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=9,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p", covariate="detection") + 
  ggtitle("scDD, Covariate 2: Detection Rate")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="detection", maxy=9,
           main = "scDD, Covariate 2: Detection Rate") 
```
## Multiple-Testing Correction

@@

### Covariate one: Mean nonzero expression

@@

if (!file.exists(res1)){
  sb1 <- bd %>% buildBench(data.frame(rowData(humandata)) %>% 
                                   filter(!is.na(scdd_p)) %>%
                                   mutate(pval=scdd_p,
                                          ind_covariate=meanExp), 
                          ftCols = c("meanExp"),
                          parallel=TRUE)

@@

if (!file.exists(res2)){
  sb2 <- bd %>% buildBench(data.frame(rowData(humandata)) %>% 
                                   filter(!is.na(scdd_p)) %>%
                                   mutate(pval=scdd_p,
                                          ind_covariate=detection), 
                          ftCols = c("detection"),
                          parallel=TRUE)

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans = "log1p") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-mouse-scdd.Rmd
Update headers, simplify p-val variable naming

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="scdd_p_combined", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)), 
           pvalue="scdd_p_combined", covariate="meanExp", maxy=20,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="scdd_p_combined", covariate="detection") + 
  ggtitle("scDD, Covariate 2: Detection Rate")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)), 
           pvalue="scdd_p_combined", covariate="detection", maxy=20,
           main = "scDD, Covariate 2: Detection Rate") 
```

@@

if (!file.exists(res1)){
  sb1 <- bd %>% buildBench(data.frame(rowData(mousedata)) %>% 
                                   na.omit() %>%
                                   mutate(pval=scdd_p_combined,
                                          ind_covariate=meanExp), 
                          ftCols = c("meanExp"),
                          parallel=TRUE)

@@

if (!file.exists(res2)){
  sb2 <- bd %>% buildBench(data.frame(rowData(mousedata)) %>% 
                                   na.omit() %>%
                                   mutate(pval=scdd_p_combined,
                                          ind_covariate=detection), 
                          ftCols = c("detection"),
                          parallel=TRUE)

>>>>

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="scdd_p", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=20,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="scdd_p", covariate="detection") + 
  ggtitle("scDD, Covariate 2: Detection Rate")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)), 
           pvalue="scdd_p", covariate="detection", maxy=20,
           main = "scDD, Covariate 2: Detection Rate") 
```

@@

if (!file.exists(res1)){
  sb1 <- bd %>% buildBench(data.frame(rowData(mousedata)) %>% 
                                   filter(!is.na(scdd_p)) %>%
                                   mutate(pval=scdd_p,
                                          ind_covariate=meanExp), 
                          ftCols = c("meanExp"),
                          parallel=TRUE)

@@

if (!file.exists(res2)){
  sb2 <- bd %>% buildBench(data.frame(rowData(mousedata)) %>% 
                                   filter(!is.na(scdd_p)) %>%
                                   mutate(pval=scdd_p,
                                          ind_covariate=detection), 
                          ftCols = c("detection"),
                          parallel=TRUE)
